Bayesian Hyper-Heuristics

### 2023-01-23 article/sections/08-results.tex
✨ (article): Conclusion done

The methodology presented a number of experimental groups to conduct. The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, and an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. This section provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}. The remainder of the chapter is structured as follows:

\begin{itemize}
	\item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the outcomes of the empirical process and highlights key aspects to observe in the results.

	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes \acp{MH} in the \index{heuristic pool}heuristic pool.

\end{itemize}

@@

Furthermore, the case study focuses on three variants of the \acs{BHH}. These include the baseline configuration, as was provided in Chapter \ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}). Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}). Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all. This section is structured as follows:

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

\end{itemize}

@@

Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process. Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used. Then for all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.

@@

The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled. The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Chapter \ref{chap:bhh}. As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.

@@

\subsection{Summary}\label{sec:results:summary}

This section provided the results of the empirical process that was described in Chapter \ref{chap:methodology}. Three experimental groups were designed. These experimental groups include a case study on the behaviour of the \acs{BHH} as it relates to an example dataset (iris). Furthermore, an experimental group that compares the performance of the \acs{BHH} to standalone, low-level \index{heuristic}heuristics was included, and finally, an experimental group that compares the effects of various hyper-parameters on the outcomes of the \acs{BHH} was also included. The empirical results for each of these experimental groups were presented in detail.

In general, it was found that the \acs{BHH} is able to successfully train the underlying \acp{FFNN}. Detailed analysis and discussions of the empirical results were provided along with illustrations for visual aid. Where possible, detailed discussions were presented that explain the reasons behind the outcomes that were produced. Throughout, various suggestions were made to improve on the implementations made in this dissertation.

Finally, all results that were presented were retrieved from statistical analysis which yield statistical certainty in the results and outcomes observed.

>>>>

This section provides the results of all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.

@@

The case study focuses on three variants of the \acs{BHH}. These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}). Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}). Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.

@@

Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.

@@

The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled. The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}. As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.

@@
